### 2024-05-19 fantasy-football.qmd
20240519 - updated formation
20240519 - concision

![An Example Football Formation for the Offense and Defense.](images/footballFormation.png){#fig-footballFormation}

@@

- Quarterback (QB)
- Running Back (RB)
    - Halfback or Tailback
    - Fullback (FB)
- Wide Receiver (WR)
- Tight End (TE)
- Offensive Line (OL)
    - Center (C)
    - Offensive Guard (OG)
    - Offensive Tackle (OT)

@@

The players on the Offensive Line block for running and passing plays.
On passing plays, they provide protection for the Quarterback so the Quarterback has time to pass the ball without being tackled.
On running plays, they provide protection for the player running the ball (e.g., the Running Back) so the ball carrier can get as far as possible without being tackled.
Players on the Offensive Line tend to be large so they can provide adequate protection for the Quarterback and Running Back.

@@

- Defensive Line (DL)
    - Defensive End (DE)
    - Defensive Tackle (DT)
- Linebacker (LB)
    - Middle (or Inside) Linebacker (MLB)
    - Outside Linebacker (OLB)
- "The Secondary" / Defensive Back (DB)
    - Cornerback (CB)
    - Safety (S)
        - Free Safety (FS)
        - Strong Safety (SS)

@@

On passing plays, the players on the Defensive Line try to apply pressure to the Quarterback and try to sack them.
On rushing plays, the players on the Defensive Line try to tackle the ball carrier.
Players on the Defensive Line tend to be large yet quick so they can apply pressure to the Quarterback.

>>>>

::: {#fig-footballFormation}
![](images/footballFormation.png)

An Example Football Formation for the Offense and Defense. The solid line indicates the line of scrimmage. The arrow indicates the direction the offense tries to advance the ball.
:::

@@

- Quarterback (QB)
- Running Back (RB)
    - Halfback or Tailback
    - Fullback (FB)
- Wide Receiver (WR)
- Tight End (TE)
- Offensive Linemen (OL)
    - Center (C)
    - Offensive Guard (OG)
    - Offensive Tackle (OT)

@@

Offensive Linemen block for running and passing plays.
On passing plays, they provide protection for the Quarterback so the Quarterback has time to pass the ball without being tackled.
On running plays, they provide protection for the player running the ball (e.g., the Running Back) so the ball carrier can get as far as possible without being tackled.
Offensive Linemen tend to be large so they can provide adequate protection for the Quarterback and Running Back.

@@

- Defensive Linemen (DL)
    - Defensive End (DE)
    - Defensive Tackle (DT)
- Linebacker (LB)
    - Middle (or Inside) Linebacker (MLB)
    - Outside Linebacker (OLB)
- "The Secondary" / Defensive Back (DB)
    - Cornerback (CB)
    - Safety (S)
        - Free Safety (FS)
        - Strong Safety (SS)

@@

On passing plays, Defensive Linemen try to apply pressure to the Quarterback and try to sack them.
On rushing plays, Defensive Linemen try to tackle the ball carrier.
Defensive Linemen tend to be large yet quick so they can apply pressure to the Quarterback.
